Boson-Sampling with Single Photons: A Roadmap to Post-Classical Computation

### 2016-09-22 paper.tex
added stub for vision section

Comparing the requisite times, we plot the critical photon-number as a function of efficiency, $\eta$, for the quantum boson-sampler to beat its classical counterpart, as shown in Fig.~\ref{fig:curves_1}(a). The right part of each line is the area of quantum supremacy. For a given single-photon efficiency, with increasing $n$, the quantum simulator's superiority becomes more prominent. Thus, scaling up the size of boson-sampling is essential to achieving this goal. But there is an upper limit. Taking \mbox{$\eta=0.4$} as an example, it is impossible to reach quantum supremacy for a classical computer of petaFLOPS by only increasing the number of single photons. A more convenient approach is to increase the efficiency of the quantum system. As the efficiency increases, the minimum photon-number required to achieve quantum supremacy decreases, simplifying experimental resource requirements.

\begin{figure}[!htb]
\includegraphics[width=\columnwidth]{curves_1}
\caption{The quantum and classical supremacy of (spatially-encoded) boson-sampling is divided by the red lines, where the top-right region corresponds to quantum supremacy and vice versa. The efficiency denoted on the horizontal axis is the overall system efficiency. (a) $R=76$MHz. The numbers 3, 6, etc. in the lines refer to $10^3\mathrm{FLOPS}$, $10^6\mathrm{FLOPS}$ etc. of the classical simulator. (b) $A=10^9\mathrm{Hz}$. The numbers 2, 3, etc. in the lines denote photon-number.} \label{fig:curves_1}
\end{figure}

@@

An alternative scheme fully employs time-bin encoding to construct the interferometer network, which was proposed \cite{bib:19} in 2014 and first demonstrated \cite{bib:11} in 2016. The main idea is to utilise the temporal degree of freedom, by applying a mapping from spatial modes to time-bins. This scheme has fixed experimental complexity and only needs one high repetition rate SPS, one time-resolved detector and one dynamic beamsplitter, which makes it much easier to align the experimental setup since there is only a single point of interference. The architecture is shown in Fig.~\ref{fig:loop_arch}.

@@

\begin{figure}[!htb]
\includegraphics[width=\columnwidth]{curves_2}
\caption{The quantum and classical supremacy of (a) temporal-encoding, and (b) hybrid-encoding boson-sampling, is divided by the red line, where quantum supremacy is in the top-right region, and vice versa. The numbers 3, 6, etc. in the line refer to $10^3$FLOPS, $10^6$FLOPS etc. of classical computers respectively. The efficiency denoted on the horizontal axis is the overall system efficiency. Given the magnitude of the coupling strength, a single step including a beam splitter operation and phase-shifting operation takes \mbox{$\tau\sim0.3\mu\mathrm{s}$} \cite{bib:20}. Effective repeat frequency (a) \mbox{$R'=1/(13\mathrm{ns}\cdot 10^4)$}, (b) \mbox{$R'=1/(0.3\mu\mathrm{s}\cdot n^2).$}} \label{fig:curves_2}
\end{figure}

@@

\begin{figure}[!htb]
\includegraphics[width=0.5\columnwidth]{curve_scattershot}
\caption{The quantum and classical supremacy of scattershot boson-sampling is separated by the red line, where the top-right region belongs to quantum supremacy and vice versa. The numbers 3, 6, etc. on the lines refer to $10^3$FLOPS, $10^6$FLOPS etc. of classical computers respectively. The efficiency denoted on the horizontal axis is the overall system efficiency except the preparation efficiency of the source, whereby the preparation efficiency of $n$ sources is substituted with $1/\sqrt{2\pi n}$ \cite{bib:36}.} \label{fig:curve_scattershot}
\end{figure}

@@

The problem of physical size \comment{???} also haunts another popular platform in the field of optical quantum information processing -- fused silica waveguides, fabricated using femtosecond laser direct-written (FLDW) technology. Unlike PLC fabrication, the FLDW is a powerful and flexible technique for rapid 3D fabrication, requiring no masking procedure or cleanroom environment. However, this one-step fabrication process also makes the propagation loss rely heavily on the motion control accuracy of the precision stage \cite{bib:63}. FLDW waveguides exhibit lowest losses on the order of 0.1dB/cm \cite{bib:63}, substantially higher than that of PLC waveguides. Also, the maximum refractive index contrast achieved so far is 1\%, which limits waveguide bends to a radius of about 15mm (see Tab.~\ref{tab:one}).

@@

>>>>

Comparing the requisite times, we plot the critical photon-number as a function of efficiency for the quantum boson-sampler to beat its classical counterpart, as shown in Fig.~\ref{fig:curves_1}(a). That is, the red lines mark the classical/quantum supremacy transition point, whereby \mbox{$\tau_q=\tau_c$}. The region to the right of each line is the regime of quantum supremacy. For a given single-photon efficiency, with increasing $n$, the quantum simulator's superiority becomes more prominent. Thus, scaling up the size of boson-sampling is essential to achieving this goal. But there is an upper limit. Taking \mbox{$\eta=0.4$} as an example, it is impossible to reach quantum supremacy for a classical computer of petaFLOPS by only increasing the number of single photons. A more convenient approach is to increase the efficiency of the quantum system. As the efficiency increases, the minimum photon-number required to achieve quantum supremacy decreases, simplifying experimental resource requirements.

\begin{figure}[!htb]
\includegraphics[width=\columnwidth]{curves_1}
\caption{The quantum and classical supremacy of (spatially-encoded) boson-sampling is divided by the red lines, which mark the transition point \mbox{$\tau_q=\tau_c$}. The top-right region corresponds to quantum supremacy and vice versa. The efficiency denoted on the horizontal axis is the overall system efficiency. (a) $R=76$MHz. The numbers 3, 6, etc. in the lines refer to $10^3\mathrm{FLOPS}$, $10^6\mathrm{FLOPS}$ etc. of the classical simulator. (b) $A=10^9\mathrm{Hz}$. The numbers 2, 3, etc. in the lines denote photon-number.} \label{fig:curves_1}
\end{figure}

@@

An alternative scheme employs time-bin encoding to construct the interferometer network, which was proposed \cite{bib:19} in 2014 and first demonstrated \cite{bib:11} in 2016. The main idea is to utilise the temporal degree of freedom, by applying a mapping from spatial modes to time-bins. This scheme has fixed experimental complexity and only needs one high repetition rate SPS, one time-resolved detector and one dynamic beamsplitter, which makes it much easier to align the experimental setup since there is only a single point of interference. The architecture is shown in Fig.~\ref{fig:loop_arch}.

@@

\begin{figure}[!htb]
\includegraphics[width=\columnwidth]{curves_2}
\caption{The quantum and classical supremacy of (a) temporal-encoding, and (b) hybrid-encoding boson-sampling, is divided by the red line, where quantum supremacy is in the top-right region, and vice versa. The numbers 3, 6, etc. in the line refer to $10^3$FLOPS, $10^6$FLOPS etc. of classical computers respectively. The efficiency denoted on the horizontal axis is the overall system efficiency. Given the magnitude of the coupling strength, a single step including a beam splitter operation and phase-shifting operation takes \mbox{$\tau\sim0.3\mu\mathrm{s}$} \cite{bib:20}. Effective repeat frequency (a) \mbox{$R'=1/(13\mathrm{ns}\cdot 10^4)$}, (b) \mbox{$R'=1/(0.3\mu\mathrm{s}\cdot n^2).$} \comment{Why aren't the curves monotonic?! It's very strange that the curves change direction as photon-number increases??}} \label{fig:curves_2}
\end{figure}

@@

\begin{figure}[!htb]
\includegraphics[width=0.5\columnwidth]{curve_scattershot}
\caption{The quantum and classical supremacy of scattershot boson-sampling is separated by the red line, where the top-right region belongs to quantum supremacy and vice versa. The numbers 3, 6, etc. on the lines refer to $10^3$FLOPS, $10^6$FLOPS etc. of classical computers respectively. The efficiency denoted on the horizontal axis is the overall system efficiency \comment{(is that efficiency per mode, or total efficiency??)} except the preparation efficiency of the source, whereby the preparation efficiency of $n$ sources is substituted with $1/\sqrt{2\pi n}$ \cite{bib:36}.} \label{fig:curve_scattershot}
\end{figure}

@@

The problem of physical size \comment{I don't understand this sentence???} also haunts another popular platform in the field of optical quantum information processing -- fused silica waveguides, fabricated using femtosecond laser direct-written (FLDW) technology. Unlike PLC fabrication, the FLDW is a powerful and flexible technique for rapid 3D fabrication, requiring no masking procedure or cleanroom environment. However, this one-step fabrication process also makes the propagation loss rely heavily on the motion control accuracy of the precision stage \cite{bib:63}. FLDW waveguides exhibit lowest losses on the order of 0.1dB/cm \cite{bib:63}, substantially higher than that of PLC waveguides. Also, the maximum refractive index contrast achieved so far is 1\%, which limits waveguide bends to a radius of about 15mm (see Tab.~\ref{tab:one}).

@@

\section{A vision for the future -- the post-classical era}

\comment{Be more bold, ambitious and futuristic. Don't just want to match and slightly improve on classical computers. We want to massively outperform the world's biggest supercomputers by orders of magnitude. Let's talk more about that regime, instead of the regime where n=4 outperforms a desktop PC. That's a really uninspiring regime to talk about. How much will technology have to improve to get us to that more ambitious level? Let's look at a Moore's Law projection and estimate where classical supercomputing is going. Then let's make a boson-sampler that's faster than the biggest supercomputer 20 years from now. Then we can actually make a claim to have entered the post-classical era!}
